Notebook of learning from ensemble labels

### 2021-08-07 docs/notebook_learn_dl_ensemble.Rmd
Update dataset parse

>>>>

- Learning rates

```
python hrlcm/fit_step_lr.py --exp_name unet_lr_01 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.1 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.01 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_0001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_00001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_000001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.00001 --gamma_lr 1 --epochs 51
```
